\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
%\vspace{-1em}

\noindent\textit{Context.} High Velocity Clouds (HVCs) are a proposed solution to how extragalactic gas enters into star-forming galaxies. However, the presence of enveloping magnetic fields is hypothesised to explain how HVCs can travel through the halo without being torn apart by ram pressure. This hypothesis, in the context of HVCs, is referred to as 'magnetic draping'.

\noindent\textit{Aims.} This report aims to detect the signature of magnetic draping in HVCs and evaluate the strength of magnetic fields enveloping HVCs - in both cases using a newly constructed rudimentary algorithm applicable to the broad range of HVCs expected to be observed in upcoming radio surveys. A secondary goal of the report is to investigate of image processing of interpolated rotation measure data to solve anticipated resolution issues with higher-quality SKA-era interpolated Faraday rotation measure data.

\noindent\textit{Data.} Faraday rotation measure data was retrieved in May 2024 from the Polarisation Sky Survey of the Universe's Magnetism (POSSUM) and HVC data was retrieved the Galactic All Sky Survey (GASS). An interpolation of legacy rotation measure data was retrieved from the Galactic Faraday rotation sky 2020.

\noindent\textit{Methods.} The Kolmogorov-Smirnov test assuming a spherical HVC morphology was used to detect magnetic draping by determining the difference between in-HVC and out-HVC rotation measure populations. Two new statistical methods to evaluate the magnitude of magnetic draping were proposed, in addition to the use of a previous method sanctioned by literature. Several image processing techniques, including Fourier analysis, were visually and statistically analysed as to their efficacy at imporving interpolated rotation measure data in the context of foreground correction.

\noindent\textit{Results.} Of 13 HVCs analysed, a magnetic field signature of 11 HVCs was found to within 99.9\% confidence. One of the proposed methods, called 'variance subtraction' displayed statistical agreement with the traditional weighted mean method. The average HVC magnetic field is an order of magnitude greater than or equal to than in simulations, at scales of 1 \textmu G. The results of the derivation should be taken with great caution, however, due to large uncertainties in resultant magnetic field estimates. A two-dimensional bandpass method was found to be adequate at preserving the rotation measure foreground, with potential for it to correct for identified errors.

\newpage 

\ % The empty page

\newpage


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paper"
%%% End: 